Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-25 methods_paper/fabl-paper.tex
outlining next steps.
working on paper.

>>>>

\subsection{Pros and Cons of the Fellegi Sunter Method}

\textcolor{red}{Notes below}

``Even if one implores mixture models with a one-to-one constraint, the Fellegi-Sunter decision rule alone may still lead to many-to-many assignments such as the work by Jaro. This led to Sadinle (2017)  incorporating this constraint into the model (as in Fortini et al., 2001, 2002; Liseo and Tancredi, 2011; Tancredi and Liseo, 2011; Larsen, 2002, 2005, 2010, 2012; Gutman et al., 2013) rather than forcing it in a post-processing step."

On the other hand, this greatly adds to the computational complexity as explored by Ted in [CITE]. Explain his paper.

In this paper, we bridge the gap between both methods, in order to propose a method that takes into account the one-to-one matching constraint, while scaling to large databases.

Next, review briefly the two approach and the important technical components we utilize for our paper.
